Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-03-19 thesis/abstract.tex
minor copyediting

Our simulations follow the evolution of an idealized, isolated low mass dwarf galaxy ($M_{\rm vir} \sim 10^{9}$~M$_{\odot}$) over $\sim$ 500 Myr timescales using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}. We implemented a new star formation routine which deposts stars individually during star formation using an assumed initial mass function. Using tabulated stellar properties, we follow the stellar feedback from each of these stars individually. For massive stars ($M_* > 8$~M$_{\odot}$) we follow their stellar winds, ionizing radiation (as followed using an adaptive ray-tracing radiative transfer method), FUV radiation which leads to photoelectric heating of dust grains, Lyman-Werner radiation which leads to H$_2$ dissociation, and core collapse supernovae. In addition, we follow the asymptotic giant branch (AGB) winds of low-mass stars ($M_* < 8$~M$_{\odot}$) and Type Ia supernovae. We investigate how this detailed model for stellar feedback regulates the properties of the ISM of this low mass dwarf galaxies, its star formation, and outflows. We find agreement with previous studies that these low mass dwarf galaxies exhibit bursty, irregular star formation histories with significant feedback driven winds.

>>>>

Our simulations follow the evolution of an idealized, isolated low mass dwarf galaxy ($M_{\rm vir} \sim 10^{9}$~M$_{\odot}$) over $\sim$ 500 Myr timescales using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}. We implemented a new star formation routine which deposts stars individually during star formation with masses sampled from an initial mass function. Using tabulated stellar properties, we follow the stellar feedback from each star. For massive stars ($M_* > 8$~M$_{\odot}$) we follow their stellar winds, ionizing radiation (as followed using an adaptive ray-tracing radiative transfer method), FUV radiation which leads to photoelectric heating of dust grains, Lyman-Werner radiation which leads to H$_2$ dissociation, and core collapse supernovae. In addition, we follow the asymptotic giant branch (AGB) winds of low-mass stars ($M_* < 8$~M$_{\odot}$) and Type Ia supernovae. We investigate how this detailed model for stellar feedback regulates the properties of the ISM of this low mass dwarf galaxies, its star formation, and outflows. We find agreement with previous studies that these low mass dwarf galaxies exhibit bursty, irregular star formation histories with significant feedback driven winds.
